---
title: "Heart Disease"
author: "Murilo Miranda"
date: "2/6/2020"
output: 
  html_document:
    toc: true # table of content true
    toc_float: true
    code_folding: hide
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    theme: united
    highlight: breezedark  # specifies the syntax highlighting style
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(kableExtra)
```

## Loading data

Only 14 attributes used:

* **age**: age in years
* **sex**: 
  + value 0: female
  + value 1: male
* **cp**: chest pain type
  + value 1: typical angina
  + value 2: atypical angina
  + value 3: non-anginal pain
  + value 4: asymptomatic
* **trestbps**: resting blood pressure (in mm Hg on admission to the hospital)
* **chol**: serum cholestoral in mg/dl
* **fbs**: fasting blood sugar > 120 mg/dl 
  + value 1: true
  + value 0: false 
* **restecg**: resting electrocardiographic results
  + value 0: normal
  + value 1: having ST-T wave abnormality (T wave inversions and/or ST elevation or * depression of > 0.05 mV)
  + value 2: showing probable or definite left ventricular hypertrophy by Estes' criteria
* **thalach**: maximum heart rate achieved
* **exang**: exercise induced angina 
  + value 1: yes
  + value 0: no
* **oldpeak**: ST depression induced by exercise relative to rest
* **slope**: the slope of the peak exercise ST segment
  + value 1: upsloping
  + value 2: flat
  + value 3: downsloping
* **ca**: number of major vessels (0-3) colored by flourosopy
* **thal**:
  + value 3: normal
  + value 6: fixed defect
  + value 7: reversable defect
* **num**: diagnosis of heart disease (angiographic disease status)
  + value 0: no presence (< 50% diameter narrowing)
  + value 1-4: presence (> 50% diameter narrowing)

```{r}
variableNames <- c("age", "sex", "cp", "trestbps", "chol", "fbs", "restecg", "thalach", "exang", "oldpeak", "slope", "ca", "thal", "num")

data <- read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/heart-disease/processed.cleveland.data", sep = ",", col.names = variableNames, na.strings = "?")

data <- as_tibble(data)
```


# Convert data types
```{r}
data <- data %>% mutate(sex = as.factor(sex), cp = as.factor(cp), fbs = as.factor(fbs), restecg = as.factor(restecg), exang = as.factor(exang), slope = as.factor(slope), thal = as.factor(thal))

# first, replace positive num-values to 1,then convert it to factor 
data <- data %>% mutate(num = replace(num, num > 0, 1)) %>% mutate(num = as.factor(num))

head(data)
```


<br>